---
title: "eds_212_day2_part2"
---

```{r}
library(tidyverse)
library(palmerpenguins)


```

## Plotting functions in ggplot2

```{r}
fx = function(x){
  3*x^2+4
}
#Geom function mark
# Just 1 and 100 in the data frame
#Create a vector with multiple elements using c()
#AES aethetic mapping x = x because the data frame only has two x variables
ggplot(data.frame(x = c(1,100)),aes(x = x) ) + geom_function(fun = fx)

```

##Partial derivative

```{r}
fxyz = expression(2*x*y + 3*(x^2) * (z^3))
dfdy = D(fxyz,'y')
dfdy
```

## Penguin plot

Use view to look up a data frame

Body mass on x and flippers on y Can also just list the titles of the columns

```{r}
ggplot(data = penguins, aes(x = penguins$body_mass_g, y = penguins$flipper_length_mm)) + geom_point() +labs(x = "Flipper length (mm",
    y = "Body mass (g)", title = "Palmers penguins dimensions")
```

Change the color of data

```{r}
ggplot(data = penguins, aes(x = penguins$body_mass_g, y = penguins$flipper_length_mm, color = 'purple')) + geom_point() +labs(x = "Flipper length (mm",
    y = "Body mass (g)", title = "Palmers penguins dimensions")
```

Change color by species color = species

AES if changing a variable for chart aesthetics (ex.species)

If changing based on a constant then it should be outside of AES Can also change the theme by adding theme\_....

```{r}
ggplot(data = penguins, aes(x = penguins$body_mass_g, y = penguins$flipper_length_mm, color = species)) + geom_point() +labs(x = "Flipper length (mm",
    y = "Body mass (g)", title = "Palmers penguins dimensions") + theme_classic()
```
